Hospital Information Technology and Physician Response

### 2021-09-15 ReadingGroupPres.tex
Updates from Overleaf

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents%[hideallsubsections]
\end{frame}

@@

\begin{alertblock}{Quality Improvement}
\begin{itemize}
    \item Patient safety improvements, physicians have decision support that could prevent unnecessary complications, etc.
    \item Significant policy push for EHR implementation with this goal in mind: HITECH Act, 2008 provided financial incentive for hospitals to implement EHRs \nocite{hitech}
\end{itemize}
\end{alertblock}

@@

\begin{frame}{Physician Burnout}
\begin{center}
    \includegraphics[scale=.4]{graphics/News Clip1.PNG}
\end{center}
\end{frame}

\begin{frame}{Physician Burnout}
\begin{center}
    \includegraphics[scale=.5]{graphics/News Clip2.PNG}
\end{center}
\end{frame}

\begin{frame}{Physician Burnout}
\begin{center}
    \includegraphics[scale=.3]{graphics/News Clip3.PNG}
\end{center}
\end{frame}

@@

Does EHR implementation affect labor market decisions of physicians, specifically where, how much, and whether or not they work?

@@

\section{Model}

\begin{frame}{Physician's Incentives}
\begin{itemize}
    \item Physician decides to work, possibly at a handful of hospitals
    \item Some proportion of these implement a new technology (an EHR)
    \item Two ways to think about the effect:
    \begin{enumerate}
        \item The EHR could impose a burden on the physician, leading them to shift work to other hospitals or lower workload
        \item The EHR could increase the physician's attachment to the implementing hospital, leading them to shift away from other hospitals and towards the EHR hospital
    \end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Physician's Incentives: reduced form}
\begin{equation*}
    share_h=f()
\end{equation*}

>>>>

\begin{frame}{Table of Contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents%[hideallsubsections]
\end{frame}

@@

\begin{alertblock}{Quality Improvement}
\begin{itemize}
    \item Improved efficiency, patient safety improvements, physicians have decision support that could prevent unnecessary complications, etc.
    \item Significant policy push for EHR implementation with these goal in mind: HITECH Act, 2008 provided financial incentive for hospitals to implement EHRs \nocite{hitech}
\end{itemize}
\end{alertblock}

@@

\begin{frame}[noframenumbering]{Physician Burnout}
\begin{center}
    \includegraphics[scale=.4]{graphics/News Clip1.PNG}
\end{center}
\end{frame}

\begin{frame}[noframenumbering]{Physician Burnout}
\begin{center}
    \includegraphics[scale=.5]{graphics/News Clip2.PNG}
\end{center}
\end{frame}

\begin{frame}[noframenumbering]{Physician Burnout}
\begin{center}
    \includegraphics[scale=.3]{graphics/News Clip3.PNG}
\end{center}
\end{frame}

@@

Does EHR implementation in hospitals affect labor market decisions of physicians, specifically where, and how much they work??

@@

\section{Model and Data}

\begin{frame}{Physician's Incentives}
\begin{itemize}
    \item Physician decides to work, possibly at a handful of hospitals
    \item Some proportion of these implement a new technology (an EHR)
    \item Two ways to think about the effect:
    \begin{enumerate}
        \item The EHR could impose a burden (cost) on the physician, leading them to shift work to other hospitals or lessen their own workload
        \item The EHR could increase the physician's attachment to the implementing hospital (through the learning of a complicated new skill), leading them to lessen work at other hospitals and increase work at EHR hospital
    \end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Physician's Incentives: Reduced Form}
\begin{equation*}
    p_{iht}=\textbf{p}()
\end{equation*}
